---
title: Manipulate data with {dplyr} and visualize it with {ggplot2}
format:
  html: 
    standalone: false
  pdf: default
  docx: default
---

```{r}
#| label: setup
#| warning: false
#| message: false

# Load the core tidyverse libraries
library(tidyverse)

# Load data about penguins
penguins <- read_csv("data/penguins.csv")
```

## Data description 

For this milestone, you'll again explore data about 333 penguins living across three islands in Antarctica. See [this website](https://allisonhorst.github.io/palmerpenguins/) for complete details about the data and the variables included.


## Recreation

### Part 1

We want to see data for only Chinstrap penguins that weigh more than 4,000 grams. Run the code below to see a table. Your task is to recreate this table.

```{r}
#| label: recreate-this-part-1
#| message: false
solution_a <- readr::read_csv("data/milestone02_a.csv")
solution_a
```

Use the chunk below to re-create the table above.

```{r}
penguins |> 
  filter(species == "Chinstrap", body_mass_g > 4000) |> 
  write_csv("data/milestone02_a.csv")
```

We want to see the average, minimum, and maximum weight (`body_mass_g`) of each penguin species. Run the code below to see a table and a plot. Your task is to recreate this table and plot

```{r}
#| label: recreate-this-part-2
#| message: false
solution_b <- readr::read_csv("data/milestone02_b.csv")
solution_b
```

Use the chunk below to re-create the table and plot above (*hints*: you'll want to use `group_by()` and `summarize()` when creating the data, and you'll want to use `geom_col()` to show the values in a plot).

```{r}
penguins |> 
  group_by(species) |> 
  summarize(mean_weight = mean(body_mass_g), min_weight = min(body_mass_g), max_weight = max(body_mass_g)) |> 
  write_csv("data/milestone02_b.csv")
```

```{r}
#| label: milestone02_b

penguins |> 
  group_by(species) |> 
  summarize(mean_weight = mean(body_mass_g), min_weight = min(body_mass_g), max_weight = max(body_mass_g)) |> 
  ggplot(aes(x = species, y = mean_weight, fill = species)) + 
  geom_col()
```


## Extension

Copy the plot above and paste it into the chunk below. Do some extra things to it, like changing the labels, changing the colors, adding a new geom, plotting a different variable from the dataset, change the theme, or whatever. This is your chance to play with the plot and make it as fancy as you want.

```{r}
#| label: extension

```


## Submission

When you're all done, click on the "Render" button at the top of this editor window to render this document to a PDF or Word file. Upload that file to Canvas.

