---
title: Workshop project
format:
  html: 
    standalone: true
  pdf: default
  docx: default
---

```{r}
#| label: setup
#| warning: false
#| message: false

# Load the core tidyverse libraries
library(tidyverse)

# Load data about penguins
penguins <- read_csv("data/penguins.csv")
```

## Data description 

For this project, you'll once again explore data about 333 penguins living across three islands in Antarctica. See [this website](https://allisonhorst.github.io/palmerpenguins/) for complete details about the data and the variables included.

## Your task: Three plots!

In milestone 1 and 2, you used the `penguins` dataset to re-create some plots, and in milestone 3 you practiced using CRAP principles to redesign an ugly poster.

In this project, you will create three plots, following these guidelines:

1. They cannot be the exact same plots you made before (though you can use your earlier plots as templates or starting places).
2. You should focus on CRAP principles. Change the colors. Use functions like `theme_bw()`, `theme_minimal()`, etc. to change the overarching theme and use `theme()` to make more specific adjustments. Make these look good.
3. At least one of the plots should use data that you manipulate with {dplyr} first (e.g. use `filter()` or `group_by() |> summarize()` or create a new column with `mutate()`, etc.).

Good luck!

### Plot 1

```{r}
#| label: plot-1


```

### Plot 2

```{r}
#| label: plot-2


```

### Plot 3

```{r}
#| label: plot-3


```
